\textbf{AprilTrack: A Particle-Filter-based AprilTag Tracker}

### 2017-10-09 paper/paper.tex
Updated abstract

	The AprilTrack algorithm proposed in this paper seeks to bridge two existing fields of research in computer vision literature: fiducial detection and monocular object tracking. With a rise in the popularity of fiducials, or artificial markers, as a source of ground-truth pose estimation for visual odometry datasets and mobile robots, there has been considerable interest in designing robust and blur-resistant fiducials. Rather than devising a new fiducial, this work attempts to improve on existing fiducials, such as the popular AprilTag marker, by augmenting fiducial detection algorithms with a particle-filter based monocular object tracker which reliably tracks a fiducial's position and orientation in six degrees of freedom, allowing for tag-based localization in situations where current detectors would be unable to do so. This novel patch-based particle filter tracking algorithm, which is extended to simulatenously track multiple tags in ego-motion scenarios, is qualitatively and quantitatively evaluated on several AprilTag sequences, demonstrating that it is capable of reliably localizing blurred tags.

>>>>

	The AprilTrack algorithm proposed in this paper bridges two existing fields of research in computer vision: the detection of fiducial markers (bar code type tags), and monocular object tracking. Visual tags are highly popular for establishing ground truth location in visual odometry experiments and on mobile robots, but detection can be difficult under rapid camera motion and in poor lighting conditions due to motion blur. In contrast with other works proposing redesigned, more blur resistant tags, we use the popular AprilTag fiducials and improve detection quality by means of a particle filter based monocular object tracker. Our algorithm is able to reliably track a fiducial's position and orientation in six degrees of freedom, allowing for tag-based localization in situations where current detectors fail. This novel patch-based particle filter tracking algorithm, which is extended to simultaneously track multiple tags in ego-motion scenarios, is qualitatively and quantitatively evaluated on several AprilTag sequences, demonstrating that it is capable of reliably localizing blurred tags.
